Visualization for Machine Perception

### 2018-03-06 PAPER/paper.tex
Update some related work.
Rough paper outline.

%% Paper title.
\title{Experiments of Cleveland and McGill for Machine Perception}

@@

%other entries to be set up for journal
\shortauthortitle{Haehn \MakeLowercase{\textit{et al.}}: Experiments of Cleveland and McGill applied to Machine Perception}
%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}

@@

\maketitle

@@

>>>>

%% Paper title.
\title{Visualization for Machine Perception}

@@

%other entries to be set up for journal
\shortauthortitle{Haehn \MakeLowercase{\textit{et al.}}: Visualization for Machine Perception}
%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}

@@

@@

\section{Experimental Setup}

\subsection{Measures}

\subsection{Classifiers}

\begin{figure}[t]
	  \includegraphics[width=\linewidth]{fish.jpg}
  \caption{The Classifiers...}
	\label{fig:classifiers}
\end{figure}

\section{Elementary Perceptual Tasks}

THe Figure 1 of Cleveland McGill

\subsection{Parametrization}

Here we show each of Figure 1 with its parametrization.

\section{Position-Angle Experiment}

This is pie chart vs bar chart

\begin{figure}[t]
	  \includegraphics[width=\linewidth]{fish.jpg}
  \caption{The Position-Angle Experiment}
	\label{fig:position_angle_experiment}
\end{figure}

\section{Position-Length Experiment}

This is the one where we estimate two selected bars compared to the longest one

\begin{figure}[t]
	  \includegraphics[width=\linewidth]{fish.jpg}
  \caption{The Position-Length Experiment}
	\label{fig:position_length_experiment}
\end{figure}

\section{Bars and Framed Rectangles Experiment}

\begin{figure}[t]
	  \includegraphics[width=\linewidth]{fish.jpg}
  \caption{The Bars and Framed Rectangles Experiment}
	\label{fig:bars_and_framed_rectangles_experiment}
\end{figure}

\subsection{Weber's Law}

\section{Results and Discussion}

Cleveland McGills Ranking - can we observe something similar?

1. Position along a common scale e.g. scatter plot

2. Position on identical but nonaligned scales e.g. multiple scatter plots

3. Length e.g. bar chart

4.Angle \& Slope (tie) e.g. pie chart

5. Area e.g. bubbles

6. Volume, density, and color saturation (tie) e.g. heatmap

7. Color hue e.g. newsmap

\section{Conclusions}

Future work: allow insights for infovis for machines
